The Calculus of Linear Constructions

### 2021-12-02 writing/draft5/draft5.tex
draft5

\subsection{Extended Reduction}
The reduction semantics for the extended language is standard, we only present the most interesting $\iota$-reduction cases.

>>>>

\subsection{Extended Reduction}
The reduction semantics for the extended language is standard \cite{cic}, we only present the most interesting $\iota$-reduction cases.
